### 2020-03-14 paper/sections/abstract.tex
improve consistency

With the growth of computer vision-based applications, an explosive amount of images have been uploaded to cloud servers that host such online computer vision algorithms, usually in the form of deep learning models. JPEG has been used as the {\em de facto} compression and encapsulation method for images. However, standard JPEG configuration does not always perform well for compressing images that are to be processed by a deep learning model, e.g., the standard quality level of JPEG leads to $50\%$ of size overhead (compared with the best quality level selection) on ImageNet under the same inference accuracy in popular computer vision models (e.g., InceptionNet and ResNet). Knowing this, designing a better JPEG configuration for online computer vision services is still extremely challenging: 1) Cloud-based computer vision models are usually a black box to end-users; thus, it is challenging to design JPEG configuration without knowing their model structures. 2) The ``optimal'' JPEG configuration is not fixed; instead, it is determined by confounding factors, including the characteristics of the input images and the model, the expected accuracy and image size, etc. In this paper, we propose a reinforcement learning (RL)-based adaptive JPEG configuration framework, AdaCompress. In particular, we design an edge (i.e., user-side) reinforcement learning agent that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures. Furthermore, we design an explore-exploit mechanism to let the framework fast switch an agent when it detects a performance degradation, mainly due to the input change (e.g., images captured across daytime and night). Our evaluation experiments using real-world online computer vision APIs from Amazon Rekognition, Face++, and Baidu Vision, show that our approach outperforms existing baselines by reducing the size of images by 1/2 -- 1/3 while the overall classification accuracy only decreases slightly; Meanwhile, AdaCompress adaptively retrains or reloads the RL agent promptly to maintain the performance.

>>>>

With the growth of computer vision-based applications, an explosive amount of images have been uploaded to cloud servers that host such online computer vision algorithms, usually in the form of deep learning models. JPEG has been used as the \emph{de facto} compression and encapsulation method for images. However, standard JPEG configuration does not always perform well for compressing images that are to be processed by a deep learning model, e.g., the standard quality level of JPEG leads to $50\%$ of size overhead (compared with the best quality level selection) on ImageNet under the same inference accuracy in popular computer vision models (e.g., InceptionNet and ResNet). Knowing this, designing a better JPEG configuration for online computer vision-based services is still extremely challenging: 1) Cloud-based computer vision models are usually a black box to end-users; thus, it is challenging to design JPEG configuration without knowing their model structures. 2) The ``optimal'' JPEG configuration is not fixed; instead, it is determined by confounding factors, including the characteristics of the input images and the model, the expected accuracy and image size, etc. In this paper, we propose a reinforcement learning (RL)-based adaptive JPEG configuration framework, AdaCompress. In particular, we design an edge (i.e., user-side) reinforcement learning agent that learns the optimal compression quality level to achieve an expected inference accuracy and upload image size, only from the online inference results, without knowing details of the model structures. Furthermore, we design an \emph{explore-exploit} mechanism to let the framework fast switch an agent when it detects a performance degradation, mainly due to the input change (e.g., images captured across daytime and night). Our evaluation experiments using real-world online computer vision-based APIs from Amazon Rekognition, Face++, and Baidu Vision, show that our approach outperforms existing baselines by reducing the size of images by 1/2 -- 1/3 while the overall classification accuracy only decreases slightly; Meanwhile, AdaCompress adaptively re-trains or re-loads the RL agent promptly to maintain the performance.

### 2020-03-14 paper/sections/conclusion.tex
improve consistency

To reduce the upload traffic load of deep learning applications, most researchers focus on modifying the deep learning model, but this does not apply to the industry because the backend deep model is usually inaccessible for users. We present a heuristic solution using an reinforcement learning based agent to decide the proper compression quality level for each image, according to the input image and the backend service. Our experiments show that for different backend deep learning cloud services and different input image sceneries, using different quality selection strategy can significantly reduce the upload file size overhead while keeping comparable accuracy. Moreover, we design the inference-estimation-querying-retraining mechanism to cope with the input image scenery change and make a proper compression selection strategy for the current scenery. Our experiment result shows that once the scenery changes, the mechanism would either reload a pre-trained agent model or retrain a new
agent intelligently to achieve lower upload file size overhead while maintaining the inference accuracy.

>>>>

To reduce the upload traffic load of deep learning applications, most researchers focus on modifying the deep learning model, but this does not apply to the industry because the backend deep model is usually inaccessible for users. We present a heuristic solution using an reinforcement learning agent to decide the proper compression quality level for each image, according to the input image and the backend service. Our experiments show that for different backend deep learning cloud services and different input image ``sceneries'', using different quality selection strategy can significantly reduce the upload file size overhead while keeping comparable accuracy. Moreover, we design the \emph{inference-estimation-querying-retraining} mechanism to cope with the input image scenery change and make a proper compression selection strategy for the current scenery. Our experiment result shows that once the scenery changes, the mechanism would either re-load a pre-trained agent model or re-train a new
agent intelligently to achieve lower upload image size overhead while maintaining the inference accuracy.
